### 2021-03-05 README.Rmd
SIMPLIFY README

<!-- [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio) -->

This repository contains the data and code for our paper:

<!-- > Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx> -->

<!-- Our pre-print is online here: -->

<!-- > Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

<!-- ### How to cite -->

<!-- Please cite this compendium as: -->

<!-- > Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

@@

The simplest way (not yet enabled) to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh///master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.

<!-- You can download the compendium as a zip from from this URL: -->
<!-- [master.zip](/archive/master.zip). After unzipping: -->
<!-- - open the `.Rproj` file in RStudio -->
<!-- - run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the -->
<!-- [DESCRIPTION](/DESCRIPTION) file). -->
<!-- - finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console -->

>>>>

This repository contains the data and code for our paper:
*Haul-out behavior and aerial survey detectability of seals in the Bering and Chukchi seas*

@@

  - [:file\_folder: paper](/analysis/paper): R Markdown source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: figures](/analysis/figures): figures generated
  - [:file\_folder: scripts](/analysis/scripts): R scripts in support of analysis.
  - [:file\_folder: templates](/analysis/templates): template files and scripts.

The **data** directory contains

  - [:file\_folder: data](/data): Data used or generated in analysis

@@

The simplest way (*not yet enabled*) to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh///master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. These Docker images can also be used locally.
